Dissertation reading notes

### 2023-07-24 Texfiles/Notes.tex
Code updates
Lots of changes

\begin{itemize}
  \item Interesting point re annuities being low because of state pension.
        I could test consumption response to forced annuitization if that is the
        case as well. I think it would just mean increased spending?

@@

  \item What is expected yield differential? D
  \item \textit{" but investigating it seriously would require data on the
          degree of actuarial unfairness in the pricing of annuities not just for
          individuals but for double or even multiple lives."} This is interesting.
        Could I compare annuitization decisions of couples and singles? Singles
        should be more likely to buy annuities if this is true.

@@

  \item Need bequest motives to get annuity rates that are observed.
  \item "See \cite{friedman_warshawsky_nber_1985} for a brief discussion of several
        of these other possible explanations." that is for other explanations for
        lack of annuitization. Had a look at this and it wasn't super useful. Just
        seemed like a first draft of the paper.

@@

@@

@@

  \item To do
        \begin{enumerate}
          \item Make julia module
          \item add gender into life cycle
          \item get subjective life expectancies -- have got the code from
                david and cormac but I think they have birth dates and death dates which
                arent included in the normal elsa data.
          \item generate correct rates of annutisation
        \end{enumerate}
\end{itemize}
\subsection{\textbf{30-06}}
\begin{itemize}

>>>>

\begin{itemize}
  \item Interesting point re annuities being low because of state pension.
        I could test consumption response to forced annuitisation if that is the
        case as well. I think it would just mean increased spending?

@@

  \item What is expected yield differential? D
  \item \textit{" but investigating it seriously would require data on the
          degree of actuarial unfairness in the pricing of annuities not just for
          individuals but for double or even multiple lives."} This is interesting.
        Could I compare annuitisation decisions of couples and singles? Singles
        should be more likely to buy annuities if this is true.

@@

  \item Need bequest motives to get annuity rates that are observed.
  \item "See \cite{friedman_warshawsky_nber_1985} for a brief discussion of several
        of these other possible explanations." that is for other explanations for
        lack of annuitisation. Had a look at this and it wasn't super useful. Just
        seemed like a first draft of the paper.

@@

        item
\end{itemize}

@@

\subsection{Saturday before due date}
\begin{itemize}
  \item Thistlethwaite and Campbell, 1960 -- RD literature
  \item Regression Discontinuity Inference with Specification Error -- Lee and Card. Seems like an interesing paper
  \item Should I use financial wealth variables at retirement instead of at interview? I guess in alot of cases I wont
        know this. I could check the differences for the people that I have pre and post for.
  \item I also need to see what happens if I include family size.
  \item Ok data work is done. Now I should need to work on julia data. I think I need to run some more subjectives
\end{itemize}

@@

  \item To do
        \begin{enumerate}
          \item Make julia module
          \item add gender into life cycle
          \item get subjective life expectancies -- have got the code from
                david and cormac but I think they have birth dates and death dates which
                arent included in the normal elsa data.
          \item generate correct rates of annuitisation
        \end{enumerate}
\end{itemize}
\subsection{\textbf{30-06}}
\begin{itemize}
